\documentclass[11pt]{report}

\setlength{\parindent}{0em}
\setlength{\parskip}{0.5em}

\usepackage{url}
\usepackage{amsmath}
\usepackage{cleveref}
\usepackage{ntheorem}
\usepackage[a4paper]{geometry}
\usepackage{pgfplots}
\usepackage{graphicx}
\usepackage{caption}
\usepackage{subcaption}
\usepackage{multirow}
\usepackage{tabularx}

\pgfplotsset{width=10cm,compat=1.9}

\begin{document}

\title{Credal Classification of Automobile Insurance Risk}
\author{Ben Willis}
\maketitle

\section*{Declaration}
This piece of work is a result of my own work except where it forms an assessment
based on group project work. In the case of a group project, the work
has been prepared in collaboration with other members of the group. Material
from the work of others not involved in the project has been acknowledged and
quotations and paraphrases suitably indicated.
\newpage

\begin{abstract}
	This project investigates how credal classification can be applied to the problem of determining automobile insurance risk.
	Automobiles are assigned a risk rating on a scale of -2 to 3 by an expert.
	In this project we start by building a simple naive Bayes classifier to use technical information about a vehicle to assign a risk rating.
	We find that this classifier has a moderate accuracy.
	We will then look at how the choice of loss function can be used to influence the classifier.
	We show that different choices for the loss function allow us to impreve different aspects of the naive Bayes classifier.
	Next we describe Zaffalon's naive credal classifier and apply it to our insurance problem.
	We compare our application of the naive credal classifier to the naive Bayes classifier as well as to some previous applications.
	We see that it offers a more cautious alternative which, when dealing with a small number of observations, often fails to isolate a class.
	Finally we show how the naive credal classifier can successfully make use of objects with missing values.
\end{abstract}

\tableofcontents

\include{1_introduction}
\include{2_nbc}
\include{3_dirichlet_prior}
\include{4_loss_functions}
\include{5(a)_imprecise_prior}
\include{5(b)_ncc}
\include{6_missing_values}
\include{7_conclusion}

\include{bibliography}

\include{appendices}

\end{document}